Elicitation Complexity via Convex Piecewise Linear Loss Functions

### 2018-10-09 jessie-writeup/jessie-writeup.tex
typo
Responded to Raf's comments and tweaked proofs

A set $\Theta \subseteq 2^{\Delta(\Y)}$ is an unlabeled property, and finite if $|\Theta| < \infty$.
Observe that $\Theta$ is a set of level sets that divide the simplex, and not a function.\raft{Careful: $\Theta$ does not need to divide anything; $\Theta = \{\emptyset\}$ is technically an unlabeled (degenerate) property}

@@

\begin{definition}\label{def:unlabeled-nonredundant}
  An elicitable, unlabeled property $\Theta$ is \emph{nonredundant} if for any full dimensional $\theta_1, \theta_2 \in \Theta$ we observe $\theta_1 \cap \theta_2 = \emptyset$ almost everywhere.
  \raft{Have not defined elicitability for unlabeled properties.  Also, what does ``almost everywhere'' mean in this context, since $\That$ is just a set of sets?  I think we just want to say that there are no distinct $\theta_1,\theta_2 \in \Theta$ such that $\theta_1 \subseteq \theta_2$.}
  \jessie{Should be equivalent to definition of nonredundancy for labeled property $\Gamma$, shown in Lemma~\ref{lem:nonredundant-defs-equivalent}.}
\end{definition}

Other notes before starting:
\begin{itemize}
\item (Assuming the metric space is $(\Delta(\Y), \rho)$, where $\rho$ is Euclidean distance, although I don't think the choice of metric matters?).
We just use this looking at interiors of level sets.
\item Using generalized Lebesgue measure on $\P \subset \reals^{|\Delta(\Y)|-1}$
\item The interior of a level set $X_r$ is defined as $\inter{X_r} = \{p \in X_r: \epsilon > 0,  \forall q \in B(\epsilon,p), r \in \argmin_r \E_q L(r,Y)\}$
\item Define the boundary of the closed set $X$ by $bd(X) := X \setminus \inter{X}$.
\item A level set $\theta$ is \emph{full-dimensional} if $dim(\aff(\theta)) = dim(P)$. 
Equivalently, $\theta$ is full-dimensional if there are distributions $p_1, p_2, \ldots, p_n \in \theta$ so that $p_1, \ldots, p_n$ are affinely independent.\raft{Careful; I think you need convexity here.  Probably you want to define full-dimensional as having nonempty interior, and prove this as a consequence of convexity.}
\item A full-dimensional level set has non-empty interior.
\end{itemize}

@@

\begin{conjecture}\label{conj:gam-prime-exists}
	Let $\Gamma$ be a nondegenerate elicitable property with a finite set of \jessie{full-dimensional} level sets \jessie{$\Theta$ so that $\bigcup_{\theta \in \Theta}\theta = \P$}.
	There exists a nondegenerate, nonredundant property $\Gamma'$ such that $\Gamma' \leq \Gamma$. 
\end{conjecture}
\begin{proof}
\emph{Assumptions used: Finite level sets, elicitability implies convex BR, i.e. differentiable a.e.}\raft{Confused by BR}

	To start, construct $\R' \subseteq \R := \{ r \in \R : \inter{\Gamma_r} \neq \emptyset \}$.
	Clearly, $\R'$ is finite (and nonempty since finitely many level sets implies at least one must have nonempty interior).
	Defining the property $\Gamma' = \Gamma\cap \R'$, we see that $\Gamma' \leq \Gamma$.
	We want to show that the constructed $\Gamma'$ is nondegenerate and nonredundant.
	As $\Gamma$ is nondegenerate, there is some report $r \in \R$ such that $r \in \Gamma(p)$.
	If $p \in \inter{\Gamma}_r$, then by construction of $\R'$, we see $r \in \R'$.
	Since level sets are closed, for distributions on the boundary of a level set, the optimal report $r \in \R'$ is still an optimal report, thus there is at least one report $r \in \R'$ such that $r \in \Gamma(p)$ for all $p \in \P$, so $\Gamma'$ is nondegenerate.

@@

\begin{lemma}\label{lem:define-trim}
	Let $\Gamma$  be a nondegenerate, elicitable property \jessie{with a finite set of level sets $\Theta$ so that $\cup_{\theta \in \Theta} \theta = \P$?}.
	There exists an unlabeled property $\Theta$ so that for all nondegenerate, nonredundant $\Gamma' \leq \Gamma$, we have $\strip(\Gamma') = \Theta := \text{trim}(\Gamma)$.
\end{lemma}

@@

	Consider two nonredundant, nondegenerate properties $\Gamma' = \Gamma \cap \R' \leq \Gamma$ and $\tilde \Gamma  = \Gamma \cap \tilde \R \leq \Gamma$.
	It is sufficient to show $\Theta' := \strip(\Gamma') = \strip(\tilde \Gamma) =: \tilde \Theta$.

@@

	As $\Gamma' \leq \Gamma$ and $\tilde \Gamma \leq \Gamma$, then for some $r \in \tilde \R$, we then see that either $\Gamma'_{r'} \subsetneq \tilde \Gamma_r$ or $\tilde \Gamma_r \subsetneq \Gamma'_{r'}$.
	Intuitively, we see this because both $\Gamma'$ and $\tilde{\Gamma}$ are restrictions of the property $\Gamma$, so every level set of a restricted property must be a superset of or equal to a level set of $\Gamma$.
%	(If the level sets are not equivalent, then the intersection $\Gamma'_{r'} \cap \tilde{\Gamma_r}$ must be lower dimensional by nonredundancy of $\Gamma'$ and $\tilde{\Gamma}$ since $\partial G$ is real-valued amost everywhere.)
	The first case contradicts nonredundancy of $\Gamma'$ and the latter contradicts nonredundancy of $\tilde \Gamma$.
	Thus, there must be some $r \in \tilde{\R}$ so that $\Gamma'_{r'} = \tilde{\Gamma_r}$, so we conclude $\Gamma'_r \in \strip(\tilde \Gamma)$.

	The other direction of inclusion follows from the same logic.
	Therefore, for all nonredundant, non-degenerate properties $\Gamma' \leq \Gamma$, we observe the unique unlabeled property $\trim(\Gamma) := \Theta = \strip(\Gamma')$.

@@

	In order to understand what $\trim(\Gamma)$ is, we use the property $\Gamma' \leq \Gamma$ constructed in Conjecture~\ref{conj:gam-prime-exists}, and suppose $\R'$ is the set such that $\Gamma' = \Gamma\cap \R'$.
	For each $\theta \in \trim(\Gamma) = \strip(\Gamma)$, there must be a report $r \in \R'$ such that $\theta = \Gamma'_r$.
	By construction, $r \in \R' \implies \inter{\Gamma'_r} = \inter{\theta} \neq \emptyset$.
	Since $\theta$ is convex (as level sets of elicitable properties are) and has nonempty interior, then \jessie{$\theta$ has positive Lebesgue measure $\implies \theta$ is affinely independent $\implies$} $\theta$ is full dimensional.

@@

%	First, we see $\Theta := \trim(\Gamma) = \strip(\Gamma')$ is nonredundant in the unlabeled definition (Definition~\ref{def:unlabeled-nonredundant}) as $\Gamma'$ is nonredundant in the labeled set from Lemma~\ref{lem:nonredundant-defs-equivalent}, since we know $\Gamma'$ is well-defined and nonredundant from Conjecture~\ref{conj:gam-prime-exists}.
%	
%	
%	
%	For contradiction:
%	Let $\theta \in \Theta$ not full-dim and non-redundant (whatever that means for an unlabeled property-- see definition \ref{def:unlabeled-nonredundant} section for proposed definition).
%	
%	We now show that every level set $\theta \in \Theta = \strip(\Gamma') = \trim(\Gamma)$ is full dimensional.
%	
%	We proceed in 2 cases for a level set $\theta \in \Theta$:
%	\begin{enumerate}
%		\item For all $\theta' \in \Theta$, $\theta \cap \theta' = \emptyset$.
%		\jessie{Doesn't this only happen when $\{\theta\} = \Theta$?}
%		
%		We know the level set $\theta$ is closed by Lemma~\ref{lem:closed-level-sets}.
%		By definition of $\R'$, for $p \in \inter{\theta}$ so that for $r_\theta = \Gamma'(p)$, there is a ball $B(\epsilon, p)$ centered around $p$ so that for every $q \in B(\epsilon, p)$, $r_\theta \in \Gamma'(q)$.
%%		(In fact, as $\Theta$ is nonredundant, we claim $r_\theta = \Gamma'(q)$. \jessie{Need to show?})
%		Therefore, the level set $\Gamma_{r_\theta} = \theta$ is full dimensional as it has nonempty interior.
%		
%		Intuitively, this can be seen since the interior of $\theta$ is nonempty by nondegeneracy of $\Gamma'$.
%		
%		\bigskip
%		\hrule
%		Other notes from meeting with Raf 9/24/18:\\
%		Use closure and nondegeneracy
%		
%		Look at subset topology? ($\tau_{\R'} := \{\R' \cap U : U \in \tau \}$.)
%		
%		\hrule
%		\item There exists a level set $\theta' \in \Theta$, $\theta \cap \theta' \neq \emptyset$.
%		
%		By nonredundancy of $\Gamma'$, we then observe nonredundancy of $\Theta$, we know that $\mu(\theta \cap \theta') = 0$.
%		We want to show that $\theta$ is full dimensional.
%		
%		For contradiction, suppose $\theta \in \trim(\Gamma)$ is not full dimensional.
%		By Conjecture~\ref{conj:gam-prime-exists}, there exists a nonredundant, nondegenerate $\Gamma' \leq \Gamma$ so that $\trim(\Gamma) = \strip(\Gamma')$.
%		Consider $\R'$ so that $\Gamma' = \Gamma \cap \R'$ as constructed in the proof of Conjecture~\ref{conj:gam-prime-exists}.
%		
%		Suppose $\theta \in \trim(\Gamma)$ is not full dimensional.
%		Then $\inter{\theta} = \emptyset$.
%		As $\trim(\Gamma) = \strip(\Gamma')$, we observe that there is a unique $r \in \R'$ so that $\Gamma'_r = \theta$.
%		However, $\inter{\theta} = \inter{\Gamma'_r} = \emptyset \implies r \not \in \R'$ by the construction of $\R'$.
%		Since $\trim(\Gamma) = \strip(\Gamma')$ \emph{for all} nonredundant, nondegenerate $\Gamma' \leq \Gamma$-- including the $\Gamma'$ constructed in the proof of Conjecture~\ref{conj:gam-prime-exists}, then we conclude $\Gamma_r = \theta \not \in \strip(\Gamma') = \trim(\Gamma)$.
%		
%		
%		\bigskip
%		\hrule
%		Other notes from meeting:\\
%		Look at expected loss/score of $\Gamma'$.
%		\hrule
%	\end{enumerate}

@@

  The following are equivalent:
  \begin{enumerate}
  \item There is a finite set $\Theta \subseteq \strip(\Gamma)$ of full-dimensonal level sets, such that: (a) $\bigcup_{\theta\in\Theta} \theta = \P$, (b) for all $\theta \in \Theta$, there exists an $r_\theta \in \R$ such that $\Gamma(p) = \{r_\theta\}$ for all $p \in \inter{\theta}$.
  \item $\trim(\Gamma)$ is finite.
  \item $\strip(\Gamma)$ is finite.
  \end{enumerate}
\end{proposition}

\begin{proof}
First, we show $2 \iff 3$ then proceed in different directions to show $1\implies 2$ and $3 \implies 1$, or something like that.

\begin{enumerate}
	\item [$3 \implies 2$]
	$\trim(\Gamma) \subseteq \strip(\Gamma)$, and if $\strip(\Gamma)$ is finite, then any subset of $\strip(\Gamma)$ is finite.

	\item[$2 \implies 3$] 
	Consider $\trim(\Gamma)$ to be finite.
%	If $\Gamma$ is nonredundant, then we are finished, as $\Gamma \leq \Gamma$ and would be nondegenerate and nonredundant, so we can say $\trim(\Gamma) = \strip(\Gamma)$.

	We know there is a nonredundant, nondegenerate $\Gamma' \leq \Gamma$ so that $\strip(\Gamma') = \trim(\Gamma)$ by Conjecture~\ref{conj:gam-prime-exists} and the definition of trim.
	We take $\Gamma'$ as constructed in Conjecture~\ref{conj:gam-prime-exists} and let $\R'$ be the set constructed in the proof of Conjecture~\ref{conj:gam-prime-exists}.
	We then want to show $\strip(\Gamma) = \strip(\Gamma') \bigcup S$, where $S$ is some finite set.
	Consider the level set $\Gamma_r$ for $r \in \R$.
	If $r \in \R'$, then $\Gamma_r \in \strip(\Gamma')$.
	If $r \not \in \R'$, then the level set $\Gamma_r$ has empty interior by construction of $\R'$.
	%\jessie{Need argument about how we can only have level sets on the boundary.}
	Since $\Gamma$ is elicitable, the Score $G(p)$ is concave.
	As $G$ is differentiable almost everywhere, every level set with nonempty interior has $|\partial G(p)| = 1$ for all $p \in \inter{\theta}$, and there is then a report $r \in \R'$ so that $\theta \in \Gamma_r$.
	Thus, we concern ourselves with the case $|\partial G(p)| > 1$.
	%If $|\partial_p G(p)| = 1$ for some $p \in\theta$, then the interior $\inter{\theta} \neq \emptyset$, implying $r \in \R'$ by closure of level sets, so we must concern ourselves with the case $|\partial_p G(p)| > 1$.
	As subgradient sets are closed, there exists a finite full dimensional set $\{\theta_i\}_{i=1}^n$ in the $\epsilon$-ball around each $p \in \theta$ so that for any $p_i \in \inter{\theta_i}$, we observe $\partial G(p_i) \neq \partial_p G(p_j)$ for all $i \neq j$ and $\partial G(p_i) = \{r_i\}$ for all $1 \leq i \leq n$.
	Additionally, as level sets are closed, we claim $p \in \Gamma{r_i}$ for all $1 \leq i \leq n$.
	Therefore, $p \in \theta \implies p \in \bigcap_{\{r_i\}_{i=1}^n} \Gamma_{r_i}$ for some $\{r_i\}_{i=1}^n \subseteq \R'$.
	As $\R'$ is finite, so is the power set $2^{\R'}$, so the set $S$ is finite.
	Therefore $\strip(\Gamma) = \strip(\Gamma') \cup S$ is finite.

\item [$1 \implies 2$]
Suppose that we define $\trim(\Gamma) = \strip(\Gamma')$ for the nonredundant, nondegenerate property $\Gamma \cap \R' = \Gamma' \leq \Gamma$ as constructed in Conjecture~\ref{conj:gam-prime-exists}.

Consider $\strip(\Gamma') = \{\Gamma_r : r \in \R'\}$, so it is sufficient to show $\R'$ is finite.
Since $\Theta$ is the set of full-dimensional level sets, and $\R'$ is defined as the set of reports corresponding to level sets with nonempty interior (i.e. full-dimensional), then $\R' = \{r_\theta\}_{\theta \in \Theta}$ is finite as $\Theta$ is finite.
(Note that $r_\theta$ is unique for each level set because of nonredundancy of $\Gamma'$.)

Therefore, $\trim(\Gamma)$ is finite.

\item [$2 \implies 1$]
Consider $\trim(\Gamma) = \Theta$.
$\Theta$ is then finite and a subset of strip by definition, and by Conjecture~\ref{conj:trim-full-dim}, every $\theta \in \Theta$ is full dimensional.
Consider that $\trim(\Gamma) = \strip(\Gamma')$, and as $\Gamma'$ is nondegenerate, then for every $p \in \P$, there is a $\theta \in \Theta$ so that $p \in \theta$, so the union of the level sets is then equal to the distribution set $\P$.
Additionally, as $\Gamma$ is elicitable, the optimal report is unique almost everywhere by concavity of the score $G$.
Therefore, if $p \in \inter{\theta}$ and the optimal report $r_\theta$ is unique almost everywhere, then as there is an $\epsilon$-ball around $p$ where every for every $p'$ in the ball, $p' \in B(\epsilon, p)$, $\Gamma(p) = \Gamma(p')$.
%Additionally, for every $\theta \in \strip(\Gamma')$, there is an $r \in \R'$ so that $\{r\} = \Gamma(p)$ for all $p \in \inter{\theta}$ by nonredundancy of $\Gamma'$ and .

@@

\begin{lemma}\label{lem:nonredundant-defs-equivalent}
	An elicitable property $\Gamma$ with finite level sets is nonredundant (in the labeled definition) $\iff$ $\strip(\Gamma)$ is nonredundant (in the unlabeled definition.)
\end{lemma}
\begin{proof}
	We show both directions.\\
	\begin{enumerate}
		\item [$\implies$]
		Let the property $\Gamma:\P \to \R$ be nonredundant.
		Then for any two reports $r, r' \in \R$ with $r \neq r'$, the level sets $\theta := \Gamma_r \not \subseteq \Gamma_{r'}$ and $\theta' := \Gamma_{r'} \not \subseteq \Gamma_r$.
		In what follows, $G : \P \to \R$ is the Bayes Risk, or optimal report given a distribution $p$.
		Each report $r$ corresponds to a labeling of the subgradient sets of $G$.

		\jessie{Doesn't really use the assumption at all... uses concavity of Bayes Risk.}

		For notation, we write the set $S := \{p \in \P : |\partial(G(p))| > 1\}$

		Then consider the set $\theta \cap \theta'$.

		%		Suppose for contradiction that $\inter{(\theta \cap \theta')} \neq \emptyset$.
		%		Then there is some $s \in \inter{(\theta \cap \theta')}$ so that $p \in B(\epsilon, s) \implies p \in \inter{(\theta \cap \theta')}$.
		%		As the ball $B(\epsilon s)$ is convex with nonempty interior, it has positive measure, and by monotonicity of a measure, we say $0 < \mu(B(\epsilon, s)) \leq \mu(\inter{(\theta \cap \theta')})$.

		Since the property $\Gamma$ is elicitable, the Bayes Risk is strictly convex-- meaning it is differentiable almost everywhere, thus $\mu(S) = 0$.

>>>>

A set $\Theta \subseteq 2^{\Delta(\Y)}$ is an unlabeled property, and finite if $|\Theta| < \infty$.
Observe that $\Theta$ is a set of level sets, and not a function.\raft{Careful: $\Theta$ does not need to divide anything; $\Theta = \{\emptyset\}$ is technically an unlabeled (degenerate) property}

@@

\begin{definition}\label{def:unlabeled-nonredundant}
  An unlabeled property $\Theta$ is \emph{nonredundant} if for there are no full dimensional level sets $\theta_1, \theta_2 \in \Theta$ so that $\theta_1 \subseteq \theta_2$.
  \raft{Have not defined elicitability for unlabeled properties.  Also, what does ``almost everywhere'' mean in this context, since $\Theta$ is just a set of sets?  I think we just want to say that there are no distinct $\theta_1,\theta_2 \in \Theta$ such that $\theta_1 \subseteq \theta_2$.- you're right... shoot}
  \jessie{Should be equivalent to definition of nonredundancy for labeled property $\Gamma$, shown in Lemma~\ref{lem:nonredundant-defs-equivalent}.}
\end{definition}

Other notes before starting:
\begin{itemize}
\item (Assuming the metric space is $(\Delta(\Y), \rho)$, where $\rho$ is Euclidean distance, although I don't think the choice of metric matters?).
We just use this looking at interiors of level sets.
\item Using generalized Lebesgue measure on $\P \subset \reals^{|\Delta(\Y)|-1}$
\item The interior of a level set $X_r$ is defined as $\inter{X_r} = \{p \in X_r: \epsilon > 0,  \forall q \in B(\epsilon,p), r \in \argmin_r \E_q L(r,Y)\}$
\item Define the boundary of the closed set $X$ by $bd(X) := X \setminus \inter{X}$.
\item A level set $\theta$ is \emph{full-dimensional} if it has nonempty interior. %% old: $dim(\aff(\theta)) = dim(\P)$. 
%Equivalently, $\theta$ is full-dimensional if there are distributions $p_1, p_2, \ldots, p_n \in \theta$ so that $p_1, \ldots, p_n$ are affinely independent.
\raft{Careful; I think you need convexity here.  Probably you want to define full-dimensional as having nonempty interior, and prove this as a consequence of convexity.}
\jessiet{What is the formal, ``official'' definition of full-dimensional, if one exists?}
%\item A full-dimensional level set has non-empty interior.
\end{itemize}

@@

\begin{conjecture}\label{conj:gam-prime-exists}
	Let $\Gamma$ be a nondegenerate elicitable property with a finite set of \jessie{full-dimensional} level sets \jessie{$\Theta$ so that $\bigcup_{\theta \in \Theta}\theta = \P$}.
%	There exists a nondegenerate, nonredundant property $\Gamma'$ such that $\Gamma' \preceq \Gamma$. 
\end{conjecture}
\begin{proof}
\emph{Assumptions used: Finite level sets, elicitability implies convex BR, i.e. differentiable a.e.}\raft{Confused by BR}

	To start, construct $\R' \subseteq \R := \{ r \in \R : \inter{\Gamma_r} \neq \emptyset \}$.
	Clearly, $\R'$ is finite (and nonempty since finitely many level sets implies at least one must have nonempty interior).
	Defining the property $\Gamma' = \Gamma\cap \R'$, we see that $\Gamma' \preceq \Gamma$.
	We want to show that the constructed $\Gamma'$ is nondegenerate and nonredundant.
	As $\Gamma$ is nondegenerate, there is some report $r \in \R$ such that $r \in \Gamma(p)$.
	If $p \in \inter{\Gamma}_r$, then by construction of $\R'$, we see $r \in \R'$.
	Since level sets are closed, for distributions on the boundary of a level set, the optimal report $r \in \R'$ is still an optimal report, thus there is at least one report $r \in \R'$ such that $r \in \Gamma(p)$ for all $p \in \P$, so $\Gamma'$ is nondegenerate.

@@

\begin{lemma}\label{lem:define-trim}
	Let $\Gamma$  be a nondegenerate, elicitable property \jessie{with a finite set of level sets $\Theta$ so that $\cup_{\theta \in \Theta} \theta = \P$?}.
	There exists an unlabeled property $\Theta$ so that for all nondegenerate, nonredundant $\Gamma' \preceq \Gamma$, we have $\strip(\Gamma') = \Theta := \text{trim}(\Gamma)$.
\end{lemma}

@@

	Consider two nonredundant, nondegenerate properties $\Gamma' = \Gamma \cap \R' \preceq \Gamma$ and $\tilde \Gamma  = \Gamma \cap \tilde \R \preceq \Gamma$.
	It is sufficient to show $\Theta' := \strip(\Gamma') = \strip(\tilde \Gamma) =: \tilde \Theta$.

@@

	As $\Gamma' \preceq \Gamma$ and $\tilde \Gamma \preceq \Gamma$, then for some $r \in \tilde \R$, we then see that either $\Gamma'_{r'} \subsetneq \tilde \Gamma_r$ or $\tilde \Gamma_r \subsetneq \Gamma'_{r'}$.
	Intuitively, we see this because both $\Gamma'$ and $\tilde{\Gamma}$ are restrictions of the property $\Gamma$, so every level set of a restricted property must be a superset of or equal to a level set of $\Gamma$.
%	(If the level sets are not equivalent, then the intersection $\Gamma'_{r'} \cap \tilde{\Gamma_r}$ must be lower dimensional by nonredundancy of $\Gamma'$ and $\tilde{\Gamma}$ since $\partial G$ is real-valued amost everywhere.)
	The first case contradicts nonredundancy of $\Gamma'$ and the latter contradicts nonredundancy of $\tilde \Gamma$.
	Thus, there must be some $r \in \tilde{\R}$ so that $\Gamma'_{r'} = \tilde{\Gamma_r}$, so we conclude $\Gamma'_r \in \strip(\tilde \Gamma)$.

	The other direction of inclusion follows from the same logic.
	Therefore, for all nonredundant, non-degenerate properties $\Gamma' \preceq \Gamma$, we observe the unique unlabeled property $\trim(\Gamma) := \Theta = \strip(\Gamma')$.

@@

	In order to understand what $\trim(\Gamma)$ is, we use the property $\Gamma' \preceq \Gamma$ constructed in Conjecture~\ref{conj:gam-prime-exists}, and suppose $\R'$ is the set such that $\Gamma' = \Gamma\cap \R'$.
	For each $\theta \in \trim(\Gamma) = \strip(\Gamma)$, there must be a report $r \in \R'$ such that $\theta = \Gamma'_r$.
	By construction, $r \in \R' \implies \inter{\Gamma'_r} = \inter{\theta} \neq \emptyset$.
	Since $\theta$ is convex (as level sets of elicitable properties are) and has nonempty interior, then \jessie{$\theta$ has positive Lebesgue measure $\implies \theta$ is affinely independent $\implies$} $\theta$ is full dimensional.

@@

%	First, we see $\Theta := \trim(\Gamma) = \strip(\Gamma')$ is nonredundant in the unlabeled definition (Definition~\ref{def:unlabeled-nonredundant}) as $\Gamma'$ is nonredundant in the labeled set from Lemma~\ref{lem:nonredundant-defs-equivalent}, since we know $\Gamma'$ is well-defined and nonredundant from Conjecture~\ref{conj:gam-prime-exists}.
%	
%	
%	
%	For contradiction:
%	Let $\theta \in \Theta$ not full-dim and non-redundant (whatever that means for an unlabeled property-- see definition \ref{def:unlabeled-nonredundant} section for proposed definition).
%	
%	We now show that every level set $\theta \in \Theta = \strip(\Gamma') = \trim(\Gamma)$ is full dimensional.
%	
%	We proceed in 2 cases for a level set $\theta \in \Theta$:
%	\begin{enumerate}
%		\item For all $\theta' \in \Theta$, $\theta \cap \theta' = \emptyset$.
%		\jessie{Doesn't this only happen when $\{\theta\} = \Theta$?}
%		
%		We know the level set $\theta$ is closed by Lemma~\ref{lem:closed-level-sets}.
%		By definition of $\R'$, for $p \in \inter{\theta}$ so that for $r_\theta = \Gamma'(p)$, there is a ball $B(\epsilon, p)$ centered around $p$ so that for every $q \in B(\epsilon, p)$, $r_\theta \in \Gamma'(q)$.
%%		(In fact, as $\Theta$ is nonredundant, we claim $r_\theta = \Gamma'(q)$. \jessie{Need to show?})
%		Therefore, the level set $\Gamma_{r_\theta} = \theta$ is full dimensional as it has nonempty interior.
%		
%		Intuitively, this can be seen since the interior of $\theta$ is nonempty by nondegeneracy of $\Gamma'$.
%		
%		\bigskip
%		\hrule
%		Other notes from meeting with Raf 9/24/18:\\
%		Use closure and nondegeneracy
%		
%		Look at subset topology? ($\tau_{\R'} := \{\R' \cap U : U \in \tau \}$.)
%		
%		\hrule
%		\item There exists a level set $\theta' \in \Theta$, $\theta \cap \theta' \neq \emptyset$.
%		
%		By nonredundancy of $\Gamma'$, we then observe nonredundancy of $\Theta$, we know that $\mu(\theta \cap \theta') = 0$.
%		We want to show that $\theta$ is full dimensional.
%		
%		For contradiction, suppose $\theta \in \trim(\Gamma)$ is not full dimensional.
%		By Conjecture~\ref{conj:gam-prime-exists}, there exists a nonredundant, nondegenerate $\Gamma' \preceq \Gamma$ so that $\trim(\Gamma) = \strip(\Gamma')$.
%		Consider $\R'$ so that $\Gamma' = \Gamma \cap \R'$ as constructed in the proof of Conjecture~\ref{conj:gam-prime-exists}.
%		
%		Suppose $\theta \in \trim(\Gamma)$ is not full dimensional.
%		Then $\inter{\theta} = \emptyset$.
%		As $\trim(\Gamma) = \strip(\Gamma')$, we observe that there is a unique $r \in \R'$ so that $\Gamma'_r = \theta$.
%		However, $\inter{\theta} = \inter{\Gamma'_r} = \emptyset \implies r \not \in \R'$ by the construction of $\R'$.
%		Since $\trim(\Gamma) = \strip(\Gamma')$ \emph{for all} nonredundant, nondegenerate $\Gamma' \preceq \Gamma$-- including the $\Gamma'$ constructed in the proof of Conjecture~\ref{conj:gam-prime-exists}, then we conclude $\Gamma_r = \theta \not \in \strip(\Gamma') = \trim(\Gamma)$.
%		
%		
%		\bigskip
%		\hrule
%		Other notes from meeting:\\
%		Look at expected loss/score of $\Gamma'$.
%		\hrule
%	\end{enumerate}

@@

  The following are equivalent:
  \begin{enumerate}
  \item There is a finite set $\Theta \subseteq \strip(\Gamma)$ of full-dimensonal level sets, such that: (a) $\bigcup_{\theta\in\Theta} \theta = \P$, (b) for all $\theta \in \Theta$, there exists an $r_\theta \in \R$ such that $\Gamma(p) = \{r_\theta\}$ for all $p \in \inter{\theta}$.
  \item $\trim(\Gamma)$ is finite.
  \item $\strip(\Gamma)$ is finite.
  \item \jessie{Added after fplc-elic.tex}
	\begin{itemize}
		\item[4.] $\trim(\Gamma)$ is finite and elicitable.
		\item[5.] There is a finite set of level sets that union to $\P$.
	\end{itemize}
  \end{enumerate}
\end{proposition}

\begin{proof}
First, we show $2 \iff 3$ then proceed in different directions to show $1\implies 2$ and $2 \implies 1$, or something like that.
Then we add some more to supplement, like $4 \iff 2$.

\begin{enumerate}
	\item [$3 \implies 2$]
	We know $\trim(\Gamma) \subseteq \strip(\Gamma)$, and if $\strip(\Gamma)$ is finite, then any subset of $\strip(\Gamma)$ is finite.

	\item[$2 \implies 3$] 
	Consider $\trim(\Gamma)$ to be finite.
%	If $\Gamma$ is nonredundant, then we are finished, as $\Gamma \preceq \Gamma$ and would be nondegenerate and nonredundant, so we can say $\trim(\Gamma) = \strip(\Gamma)$.

	We know there is a nonredundant, nondegenerate $\Gamma' \preceq \Gamma$ so that $\strip(\Gamma') = \trim(\Gamma)$ by Conjecture~\ref{conj:gam-prime-exists} and the definition of trim.
	We take $\Gamma'$ and $\R'$ as constructed in Conjecture~\ref{conj:gam-prime-exists}.
	We then want to show $\strip(\Gamma) = \strip(\Gamma') \bigcup S$, where $S$ is some finite set.
	Consider the level set $\Gamma_r$ for $r \in \R$.
	If $r \in \R'$, then $\Gamma_r \in \strip(\Gamma')$.
	If $r \not \in \R'$, then the level set $\Gamma_r$ has empty interior by construction of $\R'$.
	%\jessie{Need argument about how we can only have level sets on the boundary.}

	Since $\Gamma$ is elicitable, the score $G(p)$ is concave, thus differentiable almost everywhere (in the simplex).
	Thus, every level set with nonempty interior has $|\partial G(p)| = |\Gamma(p)| = 1$ for all $p \in \inter{\theta}$, and there is then a report $r \in \R'$ so that $\theta \in \Gamma_r$.

	Thus, we concern ourselves with the case $|\partial G(p)| > 1$.
	%If $|\partial_p G(p)| = 1$ for some $p \in\theta$, then the interior $\inter{\theta} \neq \emptyset$, implying $r \in \R'$ by closure of level sets, so we must concern ourselves with the case $|\partial_p G(p)| > 1$.
	As subgradient sets are closed, there exists a finite set of full dimensional level sets $\{\theta_i\}_{i=1}^m$ in the $\epsilon$-ball around each $p \in \theta$ so that for any $p_i \in \inter{\theta_i}$, we observe $\partial G(p_i) \neq \partial G(p_j)$ for all $i \neq j$ and $\partial G(p_i) = \Gamma(p) = \{r_i\}$ for all $1 \leq i \leq m$.
	Additionally, as level sets are closed, we claim $p \in \Gamma_{r_i}$ for all $1 \leq i \leq m$.
	Therefore, $p \in \theta \implies p \in \bigcap_{r' \in \{r_i\}_{i=1}^m} \Gamma_{r'}$ for some $\{r_i\}_{i=1}^m \subseteq \R'$.
	As $\R'$ is finite, so is the power set $2^{\R'}$, so the set $S = \{\Gamma_r : r \in \R \setminus \R' \}$ is finite.
	Therefore $\strip(\Gamma) = \strip(\Gamma') \cup S$ is finite.

\item [$1 \implies 2$]
Suppose that we define $\trim(\Gamma) = \strip(\Gamma')$ for the nonredundant, nondegenerate property $\Gamma \cap \R' = \Gamma' \preceq \Gamma$ as constructed in Conjecture~\ref{conj:gam-prime-exists}.

Consider $\strip(\Gamma') = \{\Gamma_r : r \in \R'\}$, so it is sufficient to show $\R'$ is finite.
Since $\Theta$ is the set of full-dimensional level sets, and $\R'$ is defined as the set of reports corresponding to level sets with nonempty interior (i.e. full-dimensional), then $\R' = \{r_\theta\}_{\theta \in \Theta}$ is finite as $\Theta$ is finite.
(Note that $r_\theta$ is unique for each level set because of nonredundancy of $\Gamma'$.)
Therefore, $\trim(\Gamma)$ is finite.

\item [$2 \implies 1$]
Consider $\trim(\Gamma) = \Theta$.
$\Theta$ is then finite and a subset of strip by definition, and by Conjecture~\ref{conj:trim-full-dim}, every $\theta \in \Theta$ is full dimensional.
Consider that $\trim(\Gamma) = \strip(\Gamma')$ for the property $\Gamma'$ constructed in Conjecture~\ref{conj:gam-prime-exists}, and as $\Gamma'$ is nondegenerate, then for every $p \in \P$, there is a $\theta \in \Theta$ such that $p \in \theta$, so the union of the level sets is then equal to the distribution set $\P$.
Additionally, as $\Gamma$ is elicitable, the optimal report is unique almost everywhere by concavity of the score $G$.
Therefore, if $p \in \inter{\theta}$ and the optimal report $r_\theta$ is unique almost everywhere, then as there is an $\epsilon$-ball around $p$ where every for every $p'$ in the ball, $p' \in B(\epsilon, p)$, $\Gamma(p) = \Gamma(p')$.
%Additionally, for every $\theta \in \strip(\Gamma')$, there is an $r \in \R'$ so that $\{r\} = \Gamma(p)$ for all $p \in \inter{\theta}$ by nonredundancy of $\Gamma'$ and .

@@

\begin{lemma}\label{lem:nonredundant-defs-equivalent}
	An elicitable property $\Gamma$ with finite level sets is nonredundant (in the labeled definition) $\iff$ $\strip(\Gamma)$ is nonredundant (in the unlabeled definition.)
\end{lemma}
\jessiet{Changed with new definition of unlabeled nonredundancy.  Old proof commented out- not sure if this one is sufficient.}
\begin{proof}
	If the property $\Gamma$ is nonredundant, there is a bijection $\phi:\R \toto \P$ so that $\phi(r) = \Gamma_r$ and $\phi^{-1}(\theta_i) = r_i$ for each level set $\theta_i \in \Theta = \strip(\Gamma)$.
	Therefore, if there are no $r_i, r_j$ so that $\Gamma_{r_i} \subseteq \Gamma_{r_j}$ then there are no level sets $\theta_i = \phi(r_i), \theta_j = \phi(r_j)$ so that $\theta_i \subseteq \theta_j$.

	Similarly, if there is no $\theta_i \subseteq \theta_j$, then there are labels for each $i$ so that $r_i = \phi^{-1}(\theta_i)$ and there is no distinct $i,j$ so that $\Gamma_{r_i} \subseteq \Gamma_{r_j}$ 	
	\jessie{Is this right...?}
